---
title: 'Part 2: Basic Inferential Data Analysis'
author: "Kumar Shaket"
date: "28/12/2020"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load the ToothGrowth Data
```{r}
library(datasets)
str(ToothGrowth)
data("ToothGrowth")
head(ToothGrowth)
```
## Summary
```{r}
#Identifying if there is any NA value in dataset
sum(!complete.cases(ToothGrowth))
```
This suggest there is no NA values in the dataset
```{r}
#Computing  summary of ToothGrowth Dataset
summary(ToothGrowth)
```
##Exploratory Analysis
```{r}
library(ggplot2)
```

```{r}
#Computing dose factor
ToothGrowth$dose <- as.factor(ToothGrowth$dose)
```

```{r}
#Plotting boxplot to understand how dose impact tooth length
p <- ggplot(ToothGrowth,aes(x=dose,y=len,fill=dose))+ geom_boxplot() + ggtitle("Fig1: Dispersion of tooth growth by dose")+xlab("dose in mg")+ylab("tooth length")
p
```
We can see that the higher the dose is, the longer the teeth are. We can notice that for a dose of 1 mg, the mean is nearly twice than for dose 0.5 mg. The progression is then lower when the dose is 2 mg. The position of the boxes are really different; this is a first clue for suggesting that the tooth length depends a lot of the dose.

```{r}
#plotting boxplot of delivery method of these doses impacting toothlength
p1 <- ggplot(ToothGrowth,aes(x=supp,y=len,fill=supp))+ geom_boxplot() + ggtitle("Fig1: Dispersion of tooth growth by delivery method")+xlab("Delivery Method")+ylab("Tooth Length")
p1
```
The boxes are quite similar. However, the median is much higher for Orange Juice than for Vitamin C; that means that for Orange Juice, the high values are more numerous than the low values, in comparison with Vitamin C.
## Hypothesis Tests
we will test if the delivery mode has an influence on the tooth growth. nul hypothesis H0 could be formulated as follows :

#H0 : The delivery mode of Vitamin C does not have any influence on the tooth growth
```{r}
dose <-ToothGrowth$dose
supply <- ToothGrowth$supp
len <- ToothGrowth$len
t.test(len[supply=="VC"],len[supply=="OJ"],paired = FALSE)
```
This first test shows the following :

* The p-value is 0.06, i.e. nearly the significance level α = 0.05.
* So we do not reject the null hypothesis, but as 0.05≦ p-value ≦0.1, it is not clearly obvious that we can reject the null hypothesis.
* The confidence interval contains 0, so the test is not really significant.

Now let’s try to test the influence of the dose on the tooth growth
```{r}
t.test(len[dose==0.5],len[dose==1],paired = FALSE)
```
This second test shows the following :

* The p-value is nearly 0  and hence we can reject H0
* The confidence interval doesn't contain 0 

An identical conclusion can be taken comparing the length of dose = 1 and dose = 2. This could already be detected from the boxplot above.

## Conclusion
* The dose of Vitamin C is clearly a factor of growth of the teeth.
* The delivery mode does not have much impact on the teeth growth.